Make any stupid plot you want

### 2021-01-18 draft/sections/math.tex
dropped fb down to base space

In this section, we first describe the fiber bundle spaces of data(\ref{sec:data}), graphics(\ref{sec:graphic}), and intermediate visual characteristics (\ref{sec:artist}). We then discuss the equivariant maps between data and visual characteristics (~\ref{sec:artist_nu}) and visual characteristics and graphics (~\ref{sec:artist_q}) that make up the artist.

>>>>

In this section, we describe the fiber bundle spaces of data(\ref{sec:data}), graphics(\ref{sec:graphic}), and intermediate visual characteristics (\ref{sec:artist}). We then discuss the equivariant maps between data and visual characteristics (~\ref{sec:artist_nu}) and visual characteristics and graphics (~\ref{sec:artist_q}) that make up the artist.
